Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-26 Results.tex
Figures!

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, despite substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.

@@

In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women. The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{}

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Mean moderate drinker signal vs mean between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

>>>>

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.

@@

In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women. The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in information sharing parameters. Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
\label{fig:emulated_sharing_iqr}
\end{figure}

Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights.

For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups. Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules. The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule, showing better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias.  For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling occurs.  The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which reflects the distorted utility function.

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}
\label{fig:emulated_payoff_group_iqr}
\end{figure}
